shrimp_goby_boatnoise

### 2025-03-04 ms_boatnoise_shrimp_goby.Rmd
Updating the directory naming and relevant code

```{r}
directory <- './2-data/'
```

@@

```{r}
BORIS_output <- read.csv("./2-data/BORIS_output.csv")
```

@@

```{r}
Video_codes <- read.csv("./2-data/Video_codes.csv")
```

@@

```{r}
shrimp_species <- read.csv("./2-data/species.csv")
```

@@

Restructure the data frame for easier analysis. We also write this file as **💿 final_df.csv** in the the 📁 `./2-data` folder. This is what we will use for analysis.

@@

write_csv(final_df, "./2-data/final_df.csv")
```

@@

```{r}
goby_out_plot3
ggsave("./3-figs/goby_out_plot3.jpeg", plot = goby_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
ggsave("./3-figs/goby_out_plot3.pdf", plot = goby_out_plot3, units = "px", width = 2200, height = 1400)
```

@@

shrimp_out_plot3
ggsave("./3-figs/shrimp_out_plot3.jpeg", plot = shrimp_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
ggsave("./3-figs/shrimp_out_plot3.pdf", plot = shrimp_out_plot3, units = "px", width = 2200, height = 1400)
```

@@

shrimp_contact_fig_together
ggsave("./3-figs/shrimp_contact_fig_together.png", plot = shrimp_contact_fig_together, units = "px", width = 2200, height = 1400, dpi = 300)
```

@@

```{r}
shrimp_contact_plot3
ggsave("./3-figs/shrimp_contact_plot3.jpeg", plot = shrimp_contact_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
ggsave("./3-figs/shrimp_contact_plot3.pdf", plot = shrimp_contact_plot3, units = "px", width = 2200, height = 1400)
```

@@

write_csv(model_estimates, "./2-data/model_estimates.csv")
```

@@

write_csv(goby_out_contrasts_table, "./2-data/goby_out_contrasts_table.csv")

@@

write_csv(shrimp_out_contrasts_table, "./2-data/shrimp_out_contrasts_table.csv")

@@

write_csv(shrimp_contact_contrasts_table, "./2-data/shrimp_contact_contrasts_table.csv")
```

>>>>

```{r}
directory <- './1-data/'
```

@@

```{r}
BORIS_output <- read.csv("./1-data/BORIS_output.csv")
```

@@

```{r}
Video_codes <- read.csv("./1-data/Video_codes.csv")
```

@@

```{r}
shrimp_species <- read.csv("./1-data/species.csv")
```

@@

Restructure the data frame for easier analysis. We also write this file as **💿 final_df.csv** in the the 📁 `./1-data` folder. This is what we will use for analysis.

@@

write_csv(final_df, "./1-data/final_df.csv")
```

@@

```{r}
goby_out_plot3
ggsave("./2-figs/goby_out_plot3.jpeg", plot = goby_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
ggsave("./2-figs/goby_out_plot3.pdf", plot = goby_out_plot3, units = "px", width = 2200, height = 1400)
```

@@

shrimp_out_plot3
ggsave("./2-figs/shrimp_out_plot3.jpeg", plot = shrimp_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
ggsave("./2-figs/shrimp_out_plot3.pdf", plot = shrimp_out_plot3, units = "px", width = 2200, height = 1400)
```

@@

shrimp_contact_fig_together
ggsave("./2-figs/shrimp_contact_fig_together.png", plot = shrimp_contact_fig_together, units = "px", width = 2200, height = 1400, dpi = 300)
```

@@

```{r}
shrimp_contact_plot3
ggsave("./2-figs/shrimp_contact_plot3.jpeg", plot = shrimp_contact_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
ggsave("./2-figs/shrimp_contact_plot3.pdf", plot = shrimp_contact_plot3, units = "px", width = 2200, height = 1400)
```

@@

write_csv(model_estimates, "./1-data/model_estimates.csv")
```

@@

write_csv(goby_out_contrasts_table, "./1-data/goby_out_contrasts_table.csv")

@@

write_csv(shrimp_out_contrasts_table, "./1-data/shrimp_out_contrasts_table.csv")

@@

write_csv(shrimp_contact_contrasts_table, "./1-data/shrimp_contact_contrasts_table.csv")
```
